Wikipedia WALS Feature Analysis

### 2019-07-19 surprisal/WALS_features.Rmd
correlation plot

```{r setup, include=FALSE}
library(tidyverse)
library(lingtypology)
library(feather)
library(here)
library(missMDA)
library(lsa)
library(reshape2)
library(broom)
library(janitor)
library(hexbin)
knitr::opts_chunk$set(echo = TRUE)
```

@@

```{r cosines}
unigram_cosines <- wiki %>%
  filter(language %in% sub_langs, gram == "Unigram") %>%
  select(-gram) %>% 
  column_to_rownames("language") %>%
  t() %>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, unigram_cosine, -language1) %>%
  mutate(unigram_cosine = 1 - abs(unigram_cosine))

@@

trigram_cosines <- wiki %>%
  filter(language %in% sub_langs, gram == "Trigram") %>%
  select(-gram) %>% 
  column_to_rownames("language") %>%
  t() %>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, trigram_cosine, -language1) %>%
  mutate(trigram_cosine = 1 - abs(trigram_cosine))

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(lingtypology)
library(feather)
library(here)
library(missMDA)
library(lsa)
library(reshape2)
library(broom)
library(janitor)
library(directlabels)
knitr::opts_chunk$set(echo = TRUE)

theme_set(theme_classic(base_size = 18))
```

@@

```{r cosines, eval = F}
unigram_cosines <- wiki %>%
  filter(language %in% sub_langs, gram == "Unigram") %>%
  select(-gram) %>% 
  column_to_rownames("language") %>%
  t() %>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, unigram_cosine, -language1)

@@

trigram_cosines <- wiki %>%
  filter(language %in% sub_langs, gram == "Trigram") %>%
  select(-gram) %>% 
  column_to_rownames("language") %>%
  t() %>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, trigram_cosine, -language1)

@@

```{r correlations}
correlation_data <- read_feather(here("Data/feature_cosine_spaces.feather"))

tidy_corr_data <- correlation_data %>%
  gather(gram, angle, unigram_cosine, trigram_cosine) %>%
  mutate(gram = if_else(gram == "unigram_cosine", "unigram", "trigram"))

ggplot(tidy_corr_data, aes(x = feature, y = angle, fill = gram,
                           color = gram, group = gram,
                           label = gram)) + 
  geom_smooth(method = "lm") +
  geom_jitter(alpha = .05) +
  geom_dl(method = "smart.grid") + 
  theme(legend.position = "none")

lmer(feature ~ distance * gram + (1|language1) + (1|language2),
     data = tidy_corr_data) %>%
  tidy()

```
